Profit Optimisation in Heterogeneous 2-link Parallel Games

### 2024-12-28 thesis/article.tex
Thesis: Major fixes in step dist function in Chapter 4
Fixes figure labels

% Commands for wrapping properly common expressions.
\newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
\newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Rightarrow}}
\newcommand{\LeftrightarrowArg}[1]{\stackrel{#1}{\Leftrightarrow}}
\newcommand{\NE}{\mathrm{N.E.}}
\newcommand{\as}{\mathrm{\alpha_s}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Gm}{\mathcal{G}}
\DeclareMathOperator*{\argmax}{arg\,max}
% \newcommand{\Exp}{\mathrm{Exp}}
% \newcommand{\Expect}{{\rm I\kern-.3em E}}

@@

\begin{center}
	\begin{multicols}{2}
		% Left Column: Network Graph
		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
			% Nodes
			\node[circle, draw, fill=blue!20, minimum size=1cm] (s) at (0,0) {$s$};
			\node[circle, draw, fill=blue!20, minimum size=1cm] (t) at (4,0) {$t$};

@@

\begin{definition}
	\label{definition:split_function}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^{|N|}|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
\end{definition}
We can easily see that if any flow user $p$ has $\alpha(p) = \as^{(i, j)}(t)$ then $c_i(p) = c_j(p)$.
The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money-sensitivity value.
We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
\end{definition}

@@

		Let $(t_{i_m})_{m \in \mathbb{N}}$ a decreasing sequence of tolls in link $i$, such that $t_{i_m} \rightarrow t_i$.
		We know that as a toll decreases, the link can only gain flow, which in turn makes $(x_i(t_{i_m}, t_{-i}))_{m \in \mathbb{N}}$ non-decreasing with $x_i(t_{i_m}, t_{-i}) \rightarrow x_i(t)$.
		Therefore we can define from each $t_{i_m}$ an edge player $(p_m)_{m \in \mathbb{N}}$ such that $p_m = \sup P_i(t_{i_m}, t_{-i})$, thus making the non-decreasing sequence $(p_m)_{m \in \mathbb{N}}$ with $p_m \rightarrow \sup P_i(t)$.

		Corollary \ref{corollary:split_to_alpha} gives us $\alpha(p_m) \le \as^{(i, j)}(t_{i_m}, t_{-i})$ for all $m \in \mathbb{N}$.
		If the inequality holds as equality (in which case $c_i(p_m) = c_j(p_m)$), we take $t_{i_m}^\prime = t_{i_m}$.
		Otherwise, it holds for all players in link $i$ that $c_i(p) < c_j(p)$, which means there is room to increase $t_{i_m}$ with no link users leaving the link (also no player from other links will enter a more expensive one), making the total flow remain the same.
		Since we're interested in $t_i$ values very close to $t_j$, we can safely assume that $i, j$ are consequent links in the toll ordering on links defined by $t$, and since $t_{i_m} \rightarrow t_i$ we can also assume that no $t_{i_m}$ element breaks that ordering.
		We can therefore see from Lemma \ref{lemma:split_monotonicity} that if we take $t_{i_m}^\prime > t_{i_m}$ then $\as^{(i, j)}(t_{i_m}^\prime, t_{-i}) \le \as^{(i, j)}(t_{i_m}, t_{-i})$, so we do so until we again reach the point where the most sensitive player of the link will view the $i, j$ link costs equally, i.e. $\alpha(p_m) = \as^{(i, j)}(t_{i_m}^\prime, t_{-i})$.
		That increase doesn't break the monotonicity of the sequence, since the increase will happen at most until the value of the previous sequence element is reached, for which we've already checked that the inequality from Corollary \ref{corollary:split_to_alpha} is tight.
		Therefore, the updated toll sequence $(t_{i_m}^\prime)_{m \in \mathbb{N}}$ becomes non-decreasing with $t_{i_m}^\prime \rightarrow t_i^\prime$ and it holds for all elements that
		\[\alpha(p_m) = \as^{(i, j)}(t_{i_m}^\prime, t_{-i})\]

@@

		%and the fact that $x(t)$ is continuous (TODO: ref?)
		%\footnote{Harkes et al. \cite[Lemma 3.1]{Harks_2019} prove a more general property where also $x_j(t_i^\prime, t_{-i}) \le x_j(t)$ for all $j \ne i$. Though it seems that also holds for heterogeneous users, since we don't need the latter property and proving it seems tricky, we omit it from this study.}
		%Let $(p_n)_{n \in \mathbb{N}}$ be an increasing sequence of players from $P_i(t)$, which , such that $p_n \rightarrow \sup P_i(t)$.
		%Therefore we can find a decreasing sequence of $(t_{i_n})_{i_n \in \mathbb{N}}$ with $t_{i_n} \rightarrow t_i$, such that $\max P_i(t_{i_n}, t_{-i}) = p_n$.
		%Such a $t_n$ might not be unique, though since $t_n > t_i > t_j$, link $i$ always remains the lower split.
		%If $t_n$ is unique, then from the monotonicity of $\as$ (Lemma \ref{lemma:split_monotonicity}) we get $\as^{(i, j)}(t_n, t_{-i}) = \alpha(p_n)$. 
		%Otherwise, it means there is a range of $t_n$ such that $\as^{(i, j)}(t_n, t_{-i}) \ge \alpha(p_n)$, so we select the highest one for which we get equality.

@@

All the above give us the graph for $\as$ in Figure \ref{figure:apha_simple:split_example}.
\begin{center}
\begin{tikzpicture}[x=5cm, y=2cm, every node/.style={font=\small}]
	\label{figure:apha_simple:split_example}

	% Axes
	\draw[->] (0,0) -- (1.2,0) node[right] {$t_1$};
	\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};

@@

	% Dots
	\fill[white] (0.5,4/3) ellipse (0.02 and 0.04);
	\draw[black] (0.5,4/3) ellipse (0.02 and 0.04);
	\fill[white] (0.5,5/3) ellipse (0.02 and 0.04);
	\draw[black] (0.5,5/3) ellipse (0.02 and 0.04);

	% Description
	\node[align=center] at (0.7, -0.7) {\textbf{Figure \ref*{figure:apha_simple:split_example}:} Split function of Example \ref{example:simple_alpha}};
\end{tikzpicture}
\end{center}

@@

\begin{proof}
	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^{|N|}$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ in $\Gm_1, \Gm_2$.
	Since $\Gm_2$ is homogeneous, we can use Lemma \ref{lemma:wardrop_equilibrium} to get that for any other flow $x^{(2)}$ it holds that
	\[
		\sum_{i \in N} \left(\tfrac1c \cdot \ell_i^{(1)}(x_i^{(2)}(t)) + t_i\right) \cdot \left(x_i^{(2)}(t) - x_i^{(2)}\right) \leq 0
	\]
	which is equivalent to
	\[
		\sum_{i \in N} \left(\ell_i^{(1)}(x_i^{(2)}(t)) + c t_i\right) \cdot \left(x_i^{(2)}(t) - x_i^{(2)}\right) \leq 0
	\]
	Notice that $\ell_i^{(1)}(x_i) + c t_i$ is the link cost of link $i$ for players in $\Gm_1$, given flow $x_i$ and toll $t_i$.
	Regardless of the heterogeneity of our users, since the above inequality holds, then for flow $x^{(2)}(t)$ in $\Gm_1$ it will also hold for any other flow $x_i^{(1)} = x^{(2)}$.
	It follows that any flow movement from $x^{(2)}(t)$ will again put players in links with larger link costs, making $x^{(2)}(t)$ a Nash Equilibrium for $t$ in $\Gm_1$ as well.
	Uniqueness of the equilibrium with regards to costs finally gives us $x^{(1)}(t) = x^{(2)}(t)$.
	Since the above hold for all $t \in \R_+^{|N|}$, we conclude from Definition \ref{definition:game_equivalence} that $\Gm_1, \Gm_2$ are equivalent.
\end{proof}
Intuitively, the above means that increasing the money sensitivity of the players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money-sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
We discuss more about the relation between time and money sensitivity in Chapter \ref{chapter:future_work}.

Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} gives us the following corollary.
\begin{corollary}
	\label{corollary:a_fixed_c_relation}
	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
	Then the following are true
	\begin{enumerate}[$(i)$]
		%\item $x^{(1)}(0) = x^{(2)}(0)$
		\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
		\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
		\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
	\end{enumerate}
\end{corollary}

@@

\section{Step distribution function}

Moving now to actual heterogeneous games, we will examine how the pricing game behaves when the distribution function is a step function, i.e. it takes finitely many values.
There will be a strong connection with the fixed distribution function games we studied earlier, and that connection extends beyond the step function, which is why we will prove it here for any distribution function.

\begin{lemma}
	\label{lemma:heterogenous_flow_equiv_fixed}
	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls and $x^{(1)}(t)$ the Nash equilibrium for $t$.
	Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
	Then $x^{(1)}(t) = x^{(2)}(t)$.
\end{lemma}

\begin{proof}
	From definition, $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two link costs as equal.
	Then, since the latency functions are the same between $\Gm_1, \Gm_2$, we get $x^{(1)}(t) = x^{(2)}(t)$, and since all players have money sensitivity $\as^{(1)}(t)$, they will all view the two links equally with no one wishing to change.
	We conclude that $x^{(1)}(t)$ is a Nash equilibrium for $t$ in $\Gm_2$ as well.
\end{proof}

\begin{corollary}
	\label{corollary:heterogenous_profit_equiv_fixed}
	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls, $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
	Then for each link operator $i$ it holds that $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$.
\end{corollary}

\begin{proof}
	Natural conclusion from Lemma \ref{lemma:heterogenous_flow_equiv_fixed} and the definition of $\Pi_i$.
\end{proof}

For a game with step distribution function in particular, the above mean that we can "slice" its flow and respective profit depending on the money sensitivity of each flow section, and apply the properties we investigated earlier on fixed distribution function games.
Combining it with the discussion around the values of $\as$ for different tolls, especially Theorem \ref{theorem:alpha_upper_irrelevant}, we can see that the game is played among a subset of $\alpha$ values, mirrored around the lower and upper splits.
We visualise this idea in the following example.

\begin{example}
	\label{example:a_step_simple}
	Let $([2], \ell, \alpha)$ be a heterogeneous pricing game where
	\begin{align*}
		\begin{aligned}
			\ell_1 &= x + 1 \\
			\ell_2 &= 2x
		\end{aligned}
		\qquad
		\alpha(p) =
		\begin{cases}
			1 & p \le 1 / 5 \\
			3 & p > 0
		\end{cases}&
	\end{align*}
	TODO: Add flow and profit plots for a fixed $t_{-i}$.
	In each case include all flow/profit for the game with $\alpha(p) = 1, 3$ and make bold the sub-intervals that are relevant.
\end{example}

In order to be able to describe the different profits on the different intervals of the step function, we introduce a definition of profit for a link operator within a flow section.

>>>>

% Commands for wrapping properly common expressions.
\newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
\newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Rightarrow}}
\newcommand{\LeftrightarrowArg}[1]{\stackrel{#1}{\Leftrightarrow}}
\newcommand{\NE}{\mathrm{N.E.}}
\newcommand{\as}{\mathrm{\alpha_s}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Gm}{\mathcal{G}}
\DeclareMathOperator*{\argmax}{arg\,max}
% \newcommand{\Exp}{\mathrm{Exp}}
% \newcommand{\Expect}{{\rm I\kern-.3em E}}

@@

\begin{center}
	\begin{multicols}{2}
		% Left Column: Network Graph
		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
			% Nodes
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

@@

\begin{definition}
	\label{definition:split_function}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^{|N|}|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
	In the case of $N = [2]$ where there exists only one link pair, we will simply write $\as(t)$.
\end{definition}
We can easily see that if any flow user $p$ has $\alpha(p) = \as^{(i, j)}(t)$ then $c_i(p) = c_j(p)$.
The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money-sensitivity value.
We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
\end{definition}

@@

		Let $(t_{i_m})_{m \in \N}$ a decreasing sequence of tolls in link $i$, such that $t_{i_m} \rightarrow t_i$.
		We know that as a toll decreases, the link can only gain flow, which in turn makes $(x_i(t_{i_m}, t_{-i}))_{m \in \N}$ non-decreasing with $x_i(t_{i_m}, t_{-i}) \rightarrow x_i(t)$.
		Therefore we can define from each $t_{i_m}$ an edge player $(p_m)_{m \in \N}$ such that $p_m = \sup P_i(t_{i_m}, t_{-i})$, thus making the non-decreasing sequence $(p_m)_{m \in \N}$ with $p_m \rightarrow \sup P_i(t)$.

		Corollary \ref{corollary:split_to_alpha} gives us $\alpha(p_m) \le \as^{(i, j)}(t_{i_m}, t_{-i})$ for all $m \in \N$.
		If the inequality holds as equality (in which case $c_i(p_m) = c_j(p_m)$), we take $t_{i_m}^\prime = t_{i_m}$.
		Otherwise, it holds for all players in link $i$ that $c_i(p) < c_j(p)$, which means there is room to increase $t_{i_m}$ with no link users leaving the link (also no player from other links will enter a more expensive one), making the total flow remain the same.
		Since we're interested in $t_i$ values very close to $t_j$, we can safely assume that $i, j$ are consequent links in the toll ordering on links defined by $t$, and since $t_{i_m} \rightarrow t_i$ we can also assume that no $t_{i_m}$ element breaks that ordering.
		We can therefore see from Lemma \ref{lemma:split_monotonicity} that if we take $t_{i_m}^\prime > t_{i_m}$ then $\as^{(i, j)}(t_{i_m}^\prime, t_{-i}) \le \as^{(i, j)}(t_{i_m}, t_{-i})$, so we do so until we again reach the point where the most sensitive player of the link will view the $i, j$ link costs equally, i.e. $\alpha(p_m) = \as^{(i, j)}(t_{i_m}^\prime, t_{-i})$.
		That increase doesn't break the monotonicity of the sequence, since the increase will happen at most until the value of the previous sequence element is reached, for which we've already checked that the inequality from Corollary \ref{corollary:split_to_alpha} is tight.
		Therefore, the updated toll sequence $(t_{i_m}^\prime)_{m \in \N}$ becomes non-decreasing with $t_{i_m}^\prime \rightarrow t_i^\prime$ and it holds for all elements that
		\[\alpha(p_m) = \as^{(i, j)}(t_{i_m}^\prime, t_{-i})\]

@@

		%and the fact that $x(t)$ is continuous (TODO: ref?)
		%\footnote{Harkes et al. \cite[Lemma 3.1]{Harks_2019} prove a more general property where also $x_j(t_i^\prime, t_{-i}) \le x_j(t)$ for all $j \ne i$. Though it seems that also holds for heterogeneous users, since we don't need the latter property and proving it seems tricky, we omit it from this study.}
		%Let $(p_n)_{n \in \N}$ be an increasing sequence of players from $P_i(t)$, which , such that $p_n \rightarrow \sup P_i(t)$.
		%Therefore we can find a decreasing sequence of $(t_{i_n})_{i_n \in \N}$ with $t_{i_n} \rightarrow t_i$, such that $\max P_i(t_{i_n}, t_{-i}) = p_n$.
		%Such a $t_n$ might not be unique, though since $t_n > t_i > t_j$, link $i$ always remains the lower split.
		%If $t_n$ is unique, then from the monotonicity of $\as$ (Lemma \ref{lemma:split_monotonicity}) we get $\as^{(i, j)}(t_n, t_{-i}) = \alpha(p_n)$. 
		%Otherwise, it means there is a range of $t_n$ such that $\as^{(i, j)}(t_n, t_{-i}) \ge \alpha(p_n)$, so we select the highest one for which we get equality.

@@

All the above give us the graph for $\as$ in Figure \ref{figure:alpha_simple:split_example}.
\begin{figure}
	\centering
	\begin{tikzpicture}[x=5cm, y=2cm, every node/.style={font=\small}]
		% Axes
		\draw[->] (0,0) -- (1.2,0) node[right] {$t_1$};
		\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};

@@

		% Dots
		\fill[white] (0.5,4/3) ellipse (0.02 and 0.05);
		\draw[black] (0.5,4/3) ellipse (0.02 and 0.05);
		\fill[white] (0.5,5/3) ellipse (0.02 and 0.05);
		\draw[black] (0.5,5/3) ellipse (0.02 and 0.05);
	\end{tikzpicture}
	\caption{Split function of Example \ref{example:simple_alpha}}
	\label{figure:alpha_simple:split_example}
\end{figure}

@@

\begin{proof}
	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^{|N|}$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ in $\Gm_1, \Gm_2$.
	Since $\Gm_2$ is homogeneous, we can use Lemma \ref{lemma:wardrop_equilibrium} to get that for any other flow $x^{(2)}$ it holds that
	\[
		\sum_{i \in N} \left(\tfrac1c \cdot \ell_i^{(1)}(x_i^{(2)}(t)) + t_i\right) \cdot \left(x_i^{(2)}(t) - x_i^{(2)}\right) \leq 0
	\]
	which is equivalent to
	\[
		\sum_{i \in N} \left(\ell_i^{(1)}(x_i^{(2)}(t)) + c t_i\right) \cdot \left(x_i^{(2)}(t) - x_i^{(2)}\right) \leq 0
	\]
	Notice that $\ell_i^{(1)}(x_i) + c t_i$ is the link cost of link $i$ for players in $\Gm_1$, given flow $x_i$ and toll $t_i$.
	Regardless of the heterogeneity of our users, since the above inequality holds, then for flow $x^{(2)}(t)$ in $\Gm_1$ it will also hold for any other flow $x_i^{(1)} = x^{(2)}$.
	It follows that any flow movement from $x^{(2)}(t)$ will again put players in links with larger link costs, making $x^{(2)}(t)$ a Nash Equilibrium for $t$ in $\Gm_1$ as well.
	Uniqueness of the equilibrium with regards to costs finally gives us $x^{(1)}(t) = x^{(2)}(t)$.
	Since the above hold for all $t \in \R_+^{|N|}$, we conclude from Definition \ref{definition:game_equivalence} that $\Gm_1, \Gm_2$ are equivalent.
\end{proof}
Since a heterogeneous game with a fixed distribution function is, in practice, homogeneous with regard to the flow behaviour, we will also use, when relevant, the term \textit{pseudo-heterogeneous game} to describe such flows more easily.

Intuitively, the above means that increasing the money sensitivity of all players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money-sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
We discuss more about the relation between time and money sensitivity in Chapter \ref{chapter:future_work}.

Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} leads us to the following one.
\begin{lemma}
	\label{lemma:a_fixed_c_relation}
	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
	Then the following are true
	\begin{enumerate}[$(i)$]
		%\item $x^{(1)}(0) = x^{(2)}(0)$
		\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
		\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
		\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
	\end{enumerate}
\end{lemma}

@@

\section{Step distribution function for $2$-link networks}

Moving now to other (actual) heterogeneous games, we will once again restrict our model to networks with $2$ links in order to simplify our analysis.
Even with this restriction, however, we will still uncover some vulnerabilities in reaching a Nash Equilibrium in the pricing competition game between the link operators.

If the flow's distribution function is a step function, i.e. it takes finitely many values, then the flow sensitivity is fixed in finite intervals.
This creates a strong connection with the pseudo-homogeneous games we studied earlier, and that connection is the main focus of this section.
The following lemma holds for any distribution function, so we prove them as such, and by discussing afterwards their implications for step functions we'll move to our main result.

\begin{lemma}
	\label{lemma:heterogenous_flow_equiv_fixed}
	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls and $x^{(1)}(t)$ the Nash equilibrium for $t$.
	Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a pseudo-heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
	Then the following hold
	\begin{enumerate}[$(i)$]
		\item $x^{(1)}(t) = x^{(2)}(t)$
		\item $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$ for each respective link operator $i$
	\end{enumerate}
\end{lemma}

\begin{proof}
	\begin{enumerate}[$(i)$]
		\item From Definition \ref{definition:split_function} we have that $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two link costs equally.
		So if we assume flow $x^{(1)}(t)$ in $\Gm_2$, where all players have money-sensitivity $\as^{(1)}(t)$, then all players will view the two link costs equally (latency functions and tolls are the same), which in turn means that everyone is happy with their choice.
		We conclude that $x^{(1)}(t)$ is a Nash Equilibrium for $t$ in $\Gm_2$ as well, and from the uniqueness of the equilibrium with regard to costs, we finally get $x^{(1)}(t) = x^{(2)}(t)$.
		\item Natural conclusion from $(i)$ and the definition of $\Pi_i$.
	\end{enumerate}
\end{proof}

We return our focus to step distribution functions, which we define as a function $\alpha$ which takes on a finite number of values $\alpha_1 < \alpha_2 < \dots < \alpha_m, \; m \in \N$.
From Lemma \ref{lemma:split_basic}$(ii)$ we have $\as \in [\alpha_1, \alpha_m]$ and from the overall analysis of $\as$ in Chapter \ref{chapter:split} we get that $\as$ will move continuously among a subset of $(\alpha_k)_{k \in [m]}$, mirrored around the lower splits on each link.
Lemma \ref{lemma:heterogenous_flow_equiv_fixed} shows us that in each case the game is corresponding to a pseudo-heterogeneous one with $\alpha(p) = \as(t)$, marking a clear connection with those games where $\alpha(p) \in (\alpha_k)_{k \in [m]}$.
Intuitively, it seems to make sense to "slice" the flow into intervals in which we have equivalency with one of those games.
We visualise this intuition in the following example.

\begin{example}
	\label{example:a_step_simple}
	Let $([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
	\begin{align*}
		\alpha(p) =
		\begin{cases}
			1 & p \le \tfrac15 \\
			3 & p \in \left(\tfrac15, \tfrac12\right) \\
			4 & p \ge \tfrac12
		\end{cases}&
	\end{align*}
\end{example}

\begin{center}
	\begin{multicols}{2}
		% Left Column: Network Graph
		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
			% Nodes
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

			% Description
			\node[align=center] at (2, -2) {Network of Example \ref{example:a_step_simple}};
		\end{tikzpicture}

		% Right Column: Distribution function Graph
		\begin{tikzpicture}[x=3cm, y=0.7cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
			\draw[->] (0,0) -- (0,4.2) node[above] {$\as(p)$};

			% Tick marks
			\draw (0,0) -- (0,-0.05) node[below] {$0$};
			\draw (0.2,0) -- (0.2,-0.05) node[below] {$\frac15$};
			\draw (0.5,0) -- (0.5,-0.05) node[below] {$\frac12$};
			\draw (1,0) -- (1,-0.05) node[below] {$1$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};
			\draw (0,3) -- (-0.05,3) node[left] {$3$};
			\draw (0,4) -- (-0.05,4) node[left] {$4$};

			% Function graph
			\draw[thick] (0,1) -- (0.2,1);
			\draw[thick] (0.2,3) -- (0.5,3);
			\draw[thick] (0.5,4) -- (1,4);

			% Closed / Open dots
			\fill[white] (0.2,1) ellipse (0.014 and 0.06);
			\draw[black] (0.2,1) ellipse (0.014 and 0.06);
			\fill[black] (0.2,3) ellipse (0.014 and 0.06);
			\draw[black] (0.2,3) ellipse (0.014 and 0.06);
			\fill[black] (0.5,3) ellipse (0.014 and 0.06);
			\draw[black] (0.5,3) ellipse (0.014 and 0.06);
			\fill[white] (0.5,4) ellipse (0.014 and 0.06);
			\draw[black] (0.5,4) ellipse (0.014 and 0.06);

			% Description
			\node[align=center] at (0.7, -1.7) {Distribution function of\\Example \ref{example:a_step_simple}};
		\end{tikzpicture}
	\end{multicols}
\end{center}
We can easily find that $x(0) = (2/3, 1/3)$, so from Corollary \ref{corollary:split_asymptotic_continuous} we get that the edge values of $\as$ are $\alpha(x_1(0)) = \alpha(2/3) = 4$ and $\alpha(x_2(0)) = \alpha(1/3) = 3$.
Focusing on link $1$, we fix an arbitrarily large $t_2$ and examine $t_1 - t_2$ for different values of $t_1$.
With a reasoning similar to that of Example \ref{example:simple_alpha} (since again $\alpha(0) = 1$) we get that the toll difference bounds are $t_1 - t_2 \le 2$ and $t_2 - t_1 \le 1$, which means that we can restrict our focus to $t_1 - t_2 \in [-1, 2]$.
We also know at which flows the behaviour of the network will change, which are exactly the flows where each all player of each sensitivity type are using a single link, i.e. the flows $(4/5, 1/5), (1/2, 1/2), (1/5, 4/5)$, e.g. flow $(4/5, 1/5)$ has all players with $\alpha(p) = 1$ in link $2$ and all $\alpha(p) = 3, 4$ players in link $1$, which in turn means that such a flow can only have $\as$ value between $1$ and $3$.

We focus on the edge cases.
For each flow and each relevant $\alpha$ value we can calculate the toll difference that will cause it, e.g. if we want to find the toll difference for which we get flow $x(t) = (4/5, 1/5)$ with $\as(t) = 3$, then we solve $\ell_1(4/5) + 3t_1 = \ell_2(1/5) + 3t_2 \Rightarrow t_2 - t_1 = 2/15$.
After calculating all cases we arrive at Figures \ref{figure:alpha_step:split} and \ref{figure:alpha_step:flow} which visualise respectively $\as(t)$ and $x_1(t)$ for all possible values of $t_1$.

\begin{figure}
	\centering
	\begin{tikzpicture}[x=3.4cm, y=1cm, every node/.style={font=\small}]
		% Axes
		\draw[->] (0,0) -- (-1.1,0);
		\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
		\draw[->] (0,0) -- (0,4.4) node[above] {$\as(t)$};

		% Tick marks
		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
		\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
		\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
		\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
		\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
		\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
		\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
		\draw (2,0) -- (2,-0.05) node[below] {$2$};
		\draw (0,1) -- (-0.05,1) node[left] {$1$};
		\draw (0,3) -- (0.05,3) node[right] {$3$};
		\draw (0,4) -- (-0.05,4) node[left] {$4$};

		% Function graph
		% Left side
		\draw[thick] (-1,1) -- (-2/5,1);
		\draw[thick] (-2/5,1) -- (-2/15,3);
		\draw[thick] (-2/15,3) -- (0,3);
		% Right side
		\draw[thick] (0,4) -- (1/8,4);
		\draw[thick] (1/8,4) -- (1/6,3);
		\draw[thick] (1/6,3) -- (7/15,3);
		\draw[thick] (7/15,3) -- (7/5,1);
		\draw[thick] (7/5,1) -- (2,1);

		% Dots
		\fill[white] (0,3) ellipse (0.02 and 0.066);
		\draw[black] (0,3) ellipse (0.02 and 0.066);
		\fill[white] (0,4) ellipse (0.02 and 0.066);
		\draw[black] (0,4) ellipse (0.02 and 0.066);
	\end{tikzpicture}
	\caption{Split function of Example \ref{example:a_step_simple}}
	\label{figure:alpha_step:split}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
		% Axes
		\draw[->] (0,0) -- (-1.1,0);
		\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
		\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};
